---
title: "Week 2 Workshop"
author: "YH"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Exercise with data

Download `wk2_stocks.rds` from Canvas. The data contain historical prices and volume for S&P 500 index (SPY) from the web. Read it into `R`.

```{r}
library(tidyverse)
df <- readRDS("../data/wk2_stocks.rds")
str(df)
```
## Statistics of S&P daily returns

+ The cumulative returns of the S&P index during this period is `r round(100*sum(df$SPY_returns), 2)`%.

+ The average daily returns of the S&P index during this period is `r round(100*mean(df$SPY_returns), 2)`%.

+ The standard deviation of the daily returns of the S&P index during this period is `r round(100*sd(df$SPY_returns), 2)`%.

## Prices of S&P in this period

```{r}
ggplot(data = df, aes(x = date, y = SPY_prices)) +
  geom_line() +
  theme_bw() +
  labs(x = "", y = "", title = "S&P 500 (SPY) Stock Prices")
```

## Total yearly returns of S&P from 2001 to 2023

```{r}
df %>%
  mutate(year = year(date)) %>%
  filter(year <= 2023) %>%
  group_by(year) %>%
  summarize(yr_returns = sum(SPY_returns)*100) %>%
  ggplot(aes(x = year, y = yr_returns)) +
  geom_col() +
  theme_bw() +
  labs(x = "", y = "", title = "S&P 500 (SPY) Stock Total Yearly Returns (%)")
```







